%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {Lead Architect} % Job title
    {IndiGo Airlines} % Organization
    {November 2024 - Present} % Date(s)
    {Gurugram, Haryana} % Location
    {
        Currently, I am working as a Lead Architect at IndiGo Airlines, where I help develop the SuperApp, an enterprise-based application for employees. I am also involved in the main IndiGo Airlines application, designing scalable and efficient solutions using Microsoft Azure and various technologies like React Native, JavaScript, Swift and Kotlin. My work includes ensuring system security with OAuth, JWT, and SSO, and focusing on cloud services, design patterns, and monitoring tools 
    }
\vspace{1.0em}
\cventry
    {Digital and Senior Consultant} % Job title
    {StatusNeo (Onsite IndiGo Airlines)} % Organization
    {September 2022 - November 2024} % Date(s)
    {Gurugram, Haryana} % Location
    {
        I was working as a Digital Consultant at StatusNeo, developing applications using React Native, TypeScript, React-Native-Paper and other libraries.
    }
\vspace{1.0em}
\cventry
    {Software Engineer} % Job title
    {Expertrons Ltd} % Organization
    {September 2021 - September 2022} % Date(s)
    {Mumbai, Maharashtra} % Location
    {
        I was working as a front end developer at Expertrons, developing, enhancing and implementing new features on iOS and Android application using React Native, I have worked with my team and contributed in increasing the crash free rate from 80\% to 98\%
    }
\vspace{1.0em}
\cventry
    {Software Engineer} % Job title
    {EkAnek Networks Pvt. Ltd.} % Organization
    {July 2020 - August 2021} % Date(s)
    {Delhi} % Location
    {
        Worked as a front end developer at EkAnek Networks Pvt. Ltd. I worked on both Foxy and Foxy Live applications using different programming languages like Swift and JavaScript framework which is React Native.
    }
\vspace{1.0em}
\cventry
    {Intern} % Job title
    {BNP Paribas} % Organization
    {Jan 2020 - June 2020} % Date(s)
    {Mumbai, Maharashtra} % Location
    {
        Analysed data from Data Warehouse using Business Intelligence Tools like SAP Business Objects and PowerBI.
    }
  \vspace{1.0em}
  \cventry
    {iOS Application Developer} % Job title
    {Petopeco Ads. Technologies} % Organization
    {Feb 2019 - May 2019} % Date(s)
    {Mumbai, Maharashtra} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Worked as an intern on product Adzlok.com, Solely responsible for development of alpha version of iOS application
        \item Adzlok is a C2C Advertising Marketplace which connects advertisers and publishers.
      \end{cvitems}
    }
\end{cventries}
