%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

\cventry
    {Lead Architect}
    {IndiGo SuperApp \tiny(Azure AD, InTune, Jenkins, RedHat, OCP, 3Scale)} % Event
    {} % Date(s)
    {} % Location
    {
        As a Lead Architect, I design enterprise applications using Microsoft technologies, create HLD/LLD documents, conduct feasibility checks, and ensure all requirements are met. I address complex architectural challenges to deliver scalable, efficient systems that align with business goals.
        \newline Roles and responsibilities:
        \begin{itemize}
            \item Lead the creation of high-level and low-level designs, documenting the architecture and solutions to guide development teams.
            \item Evaluate the feasibility of proposed solutions, considering technical and business constraints, and identify potential risks early.
            \item Work closely with stakeholders to gather and understand requirements, converting business needs into scalable and efficient technical solutions.
            \item Handle intricate and large-scale system architectures, ensuring they are optimized for performance, integration, and scalability.
            \item Mentor development teams, ensuring architectural guidelines are followed, and communicate technical decisions to stakeholders effectively.
        \end{itemize}
    }

\cventry
    {Digital and Senior Digital Consultant}
    {IndiGo SuperApp \tiny(React Native, Java, Objective-C, Swift)} % Event
    {} % Date(s)
    {} % Location
    {
        Developing application for employees of IndiGo to showcase profile where they can get all the features at one place, like leave tracking, cab and flight booking. My current tasks includes to developing and integrating multiple modules (like e-commerce, HRMS) as requested by client.
        \newline Roles and responsibilities:
        \begin{itemize}
            \item Providing consultancy to client as per requirements and features requested by client.
            \item Doing peer-to-peer code reviews.
            \item Communicating with third party vendors to implement features seamlessly.
            \item Taking ownership of the features developed and making sure to deliver them on time.
        \end{itemize}
    }

%---------------------------------------------------------
  \cventry
    {Front end developer}
    {Expertrons \tiny(React Native, Java, Objective-C, Swift)} % Event
    {} % Date(s)
    {} % Location
    {
        Expertrons is Netflix for Careers. It's the world's largest library of career videobots of experts who have shared their experience of landing a dream career like a job, internship or even a B-school. Aspirants can get connected to AI recommended experts and also get hired through a referral. 
        \newline Roles and Responsibilities: \begin{itemize}
            \item Interacting with product and marketing team and gathering requirements and make tasks to distribute in team.
            \item I was leading team of 3 front end developers to achieve tasks provided by product team.
            \item Did peer-to-peer code reviews and daily internal sync up to get status of completed tasks.
            \item I have even developed Premium features for the aspirants and experts like live video streaming from mobile application and with the same they can give online assessments, quiz and read relevant articles provided to each aspirant as per their skills.
        \end{itemize} 
    }


%---------------------------------------------------------
  \cventry
    {Front end developer}
    {Foxy Live \tiny(Swift)} % Event
    {} % Date(s)
    {} % Location
    {
        Foxy Live is India\textquotesingle s first live video streaming and social commerce platform that allows expert beauty advisors to assist you through your entire online shopping experience, all from the comfort of your own home. \newline Roles and Responsibilities: 
        \begin{itemize}
            \item My tasks included integrating third party libraries end-to-end for video calling and real time messaging so that advisor and customer can interact seamlessly. 
            \item I have provided demo to multiple advisors on how to use application and to get most out of it.
        \end{itemize} 
    }
    


%---------------------------------------------------------
  \cventry
    {Front end developer}
    {Foxy \tiny(React Native, Java, Objective-C, Swift)} % Event
    {} % Date(s)
    {} % Location
    {
        FOXY is India\textquotesingle s first beauty social commerce app for both men and women where consumers can buy beauty products which are personalised for them based on their skin type, skin tone, hair type and many other attributes. \newline Roles and Responsibilities: \begin{itemize}
            \item Interacting with Product team to gather requirements, provide technical inputs, implement the pixel perfect designs
            \item Giving demo to product team of the design and features implemented
            \item Worked closely with marketing team as well to provide them better understanding of the Firebase analytics events which will help in marketing
            \item I have worked on multiple features across the application like Facial analysis, integrating third party libraries and connecting to third party vendors regarding the issues and requirements faced at time of development.
        \end{itemize}
    }



% 

%---------------------------------------------------------
  \cventry
    {Front end developer}
    {Personal Website \tiny(ReactJS, NextJS)} % Event
    {} % Date(s)
    {} % Location
    {
        The website mrinalmaheshwari.com which is basically my personal profile where I have showcased all the related skills I have and tools and technologies I have worked on, it is created by me using ReactJS and NextJS.
    }
% \vspace{0.7em}

%---------------------------------------------------------
%   \cventry
%     {Front end and database developer}
%     {Read The Alphabets \tiny(Unity, C\#)} % Event
%     {August 2018 -- November 2018} % Date(s)
%     {} % Location
%     {
%         Read the Alphabets is a game to help anyone learn and understand new languages in a fun way, by showing them jumbled words one by one on screen and then and in the end asking them to make meaningful sentence out of that so that they can understand faster which will help them gaining knowledge and with games they can learn fast.
%     }
% \vspace{0.5em}
% %---------------------------------------------------------

% \cventry
%     {Front end and database developer}
%     {Hit the Ball \tiny(Unity, C\#)}
%     {August 2018 -- November 2018}
%     {}
%     {
%         Hit the ball is a game built in unity to teach students using multiple choice questions with graphics and animation where student can click on correct answer and let the ball roll out, if the selected answer is wrong ball bursts.
%     }
% \vspace{0.5em}
%---------------------------------------------------------

% \cventry
%     {Front end developer}
%     {Feedback System \tiny(HTML, CSS)}
%     {September 2017 -- December 2017}
%     {}
%     {
%         A platform which enabled faculty to take anonymous feedback from students using a web portal while also maintaining a record who didn't gave the feedback, making it easier to get feedback. The Head of Department can view which faculty has made the feedback form and can see the student who hadn’t replied to that form.
%     }
% \vspace{0.5em}
%---------------------------------------------------------

% \cventry
%     {Front end developer}
%     {Cavorts 2K16 \tiny(Swift)}
%     {October 2016}
%     {}
%     {
%      Created iOS application for the Sports event at Birla Institute of Technology, Mesra to make registration system more easier and paperless, with 2000+ downloads.
%     }

\end{cventries}